Web Service Community \\ Learning

### 2014-05-20 papers/webservice-coalition-learning/webservice_coalition_learning.tex
changes

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Efficient Coalition Formation \\ for Web Services}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%
%
%\IEEEcompsocitemizethanks is a special \thanks that produces the bulleted
% lists the Computer Society journals use for "first footnote" author
% affiliations. Use \IEEEcompsocthanksitem which works much like \item
% for each affiliation group. When not in compsoc mode,
% \IEEEcompsocitemizethanks becomes like \thanks and
% \IEEEcompsocthanksitem becomes a line break with idention. This
% facilitates dual compilation, although admittedly the differences in the
% desired content of \author between the different types of papers makes a
% one-size-fits-all approach a daunting prospect. For instance, compsoc
% journal papers have the author affiliations above the "Manuscript
% received ..."  text while in non-compsoc journals this is reversed. Sigh.

@@

% for Computer Society papers, we must declare the abstract and index terms
% PRIOR to the title within the \IEEEcompsoctitleabstractindextext IEEEtran
% command as these need to go into the title area created by \maketitle.
\IEEEcompsoctitleabstractindextext{%
\begin{abstract}
%\boldmath
Web services are loosely-coupled business applications willing to
cooperate in distributed settings within different groups called
communities. Communities aim to provide better visibility,
efficiency, market share and total payoff. There are a number of
proposed mechanisms and models on aggregating web services and
making them cooperate within their communities. However, forming
optimal and stable communities as coalitions to maximize
individual and group efficiency and income has not been addressed
yet. In this paper, we propose an efficient coalition formation
mechanism using cooperative game-theoretic techniques. We propose
a mechanism for community membership requests and selections of
web services under two scenarios where: (1) there is interaction between one community and many web services
and (2) web services can join multiple established communities. The ultimate objective is to
develop a mechanism for web services to form stable groups
allowing them to maximize their efficiency and generate
near-optimal (welfare-maximizing) communities. The theoretical and
extensive simulation results show that our algorithms provide web services
and community owners, in real-world like environments, with applicable and near-optimal decision
making mechanisms.
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the journal you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals frown on math
% in the abstract anyway. In particular, the Computer Society does
% not want either math or citations to appear in the abstract.

@@

\section{Introduction and Related Work}

\IEEEPARstart{O}{ver} the past years, online services have become part of many
scalable business applications. The increasing reliance on
web-based applications has significantly influenced the way web
services are engineered. Web services provide a set of stateless
software functions accessible at a network address over the web.
The recent developments are shifting web services from passive and
individual components to autonomous and group-based components
where interaction, composition, and cooperation are the key
challenges \cite{ICWS2011-1,SCC2011-1}. The main objective is to
achieve a seamless integration of business processes, applications
and web services. Delivering high quality services considering the
dynamic and unpredictable nature of the Internet is still a very
critical and challenging issue.

The need for highly available and responsive services has called
for grouping and collaborative mechanisms of loosely-coupled web
services, particularly in business settings. The idea of grouping
web services within communities and the way those communities are
engineered so that web services can better collaborate have been
proposed and investigated in
\cite{DBLP:journals/ijebr/MaamarSTBB09,DBLP:journals/internet/BenatallahSD03,Rosario:2008:PQS:1512146.1512290}.
Communities are virtual groups of web services having similar
functionalities \cite{Zeng:2003:QDW:775152.775211, Paik:2005:TSS:2229263.2230038,Medjahed05adynamic,10.1109/ARES.2008.7}, but probably different non-functional quality
attributes, which form the QoS parameters. When communities are
used, users send their requests to the masters of those
communities, which are responsible of managing the communities,
forwarding the requests to the suitable member web services and
checking the credentials of those members. Communities aim to
provide higher service availability and performance than what
individual web services can provide. The high availability of
services and the community resilience to failure are guaranteed
since web services can cooperate and replace each other within the
same community and since there is no single point of failure in
the communities architecture.

Most of the recent work on communities of services are either
user-centric and focus on user satisfaction
\cite{Chun02user-centricperformance} or system-centric and focus
on the whole system throughput, performance and utilization. There
are many contributions in distributed, grid, cluster and cloud
services which are system-centric. However, in real world
environments and applications, both users and service providers
are self-interested agents, aiming to maximize their own profit.
In those environments, both parties (users and services) will
collaborate as long as they are getting more benefits and payoff.

In this direction, recently \cite{DBLP:conf/IEEEscc/LimTMB12,
DBLP:conf/IEEEscc/KhosravifarABT11, 10.1109/TSC.2012.12} proposed mechanisms to help
users and services to maximize their gain. A two-player
non-cooperative game between web services and community master was
introduced in \cite{DBLP:conf/IEEEscc/KhosravifarABT11}. In this
game-theoretic model, the strategies available to a web service
when facing a new community are requesting to join the community,
accepting the master's invitation to join the community, or
refusing the invitation to join. The set of strategies for
communities are inviting the web service or refusing the web
service's join request. Based on their capacity, market share and
reputation, the two players have different set of utilities over
the strategy profiles of the game. The main limits of this game
model are: 1) its consideration of only three quality parameters,
while the other factors are simply ignored; and 2) the
non-consideration of the web services already residing within the
community. The game is only between the community master and the
new web service, and the inputs from all the other members are
simply ignored. The consideration of those inputs is a significant
issue as existing web services can lose utility or payoff because
of the new member, which can results in an unhealthy and unstable
group. The problem comes from the fact that the existing members
should collaborate with the new web services, so probably their
performance as a group can suffer. Existing members may even
deviate and try to join other communities if they are unsatisfied.
Those considerations of forming stable and efficient coalitions
are the main contributions of our paper.

In \cite{DBLP:conf/IEEEscc/LimTMB12}, a 3-way satisfaction approach
for selecting web services has been proposed. In this approach,
the authors proposed a web service selection process that the
community masters can use. The approach considers the efficiency
of all the three involved parties, namely users, web services and
communities. In this work, it is shown how the gains of these
parties are coupled together using a linear optimization process.
However, the optimization problem in this solution tends to
optimize some parameters considering all web services regardless
of their efficiency and contribution to the community's welfare.
Moreover, there are no clear thresholds for accepting or rejecting
new web services. The solution of the optimization problem could,
for instance, suggest web services already residing within the
community to increase or decrease their capacity to cover up the
weakness of other parties in the system. However, a high
performing web service could deviate anytime it finds itself
unsatisfied within the community instead of adjusting its service
parameters.

In \cite{10.1109/TSC.2012.12}, a cooperative scheme among autonomous
web services based on coalitional game theory has been introduced. They have proposed an algorithm to
reach individually stable coalition partition for web services in order to
maximize their efficiency. The communities choose new web services on the promise
that it would benefit the community without decreasing any other web service's
income. In their model, the worth of community is evaluated with high emphasis on
availability metric and considering price and cost values only. The community structure is based on a coordination chain,
where a web service is assigned as a \emph{primary} web service and the community task destribution
method, will initially invoke the primary web service and only if the primary web service is unavailable
will invoke the next backup web services as they are ordered in the coordination chain. However in cooperative models, it is preferred to
have a real and active cooperative activity engaging all agents to perform the tasks more efficiently. Especially nowadays
with recent advancement in cloud and hardware infrastructures availability is becoming less of an issue. So the backup web services
in their model have a very low chance of getting jobs, especially the ones further in chain, which is huge waste of web services
capabilities.

\textbf{Contributions.} In this paper, we use game theory to
propose a cooperative game model for the aggregation of web
services within communities. The solution concepts of our
cooperative game seeks to find efficient ways of forming
coalitions (teams) of web services so that they can maximize their
gain and payoff, and distribute the gain in a fair way among all
the web services. Achieving Fairness when the gain is distributed
among the community members is the main factor to keep the
coalition stable as no web service will expect to gain better by
deviating for the community. In other words, the coalition is made
efficient if all the members are satisfied. We first propose a
representation function for communities of web services based on
their QoS attributes. By using this function, we can evaluate the
$worth$ of each community of web services. When facing new
membership requests, a typical community master checks whether the
new coalition having the old and new set of web services will keep
the community stable or not. The community master will reject the
membership requests if it finds out that the new coalition would
be unstable, preventing $any$ subset of web services from gaining
significantly more by deviating from the community and joining
other communities or forming new ones. The computation of
solutions for cooperative game theory problems is combinatorial in
nature and proven to be NP-complete \cite{Algorithmic}, making
this computation impractical in real world applications. However,
using the concepts of coalition stability, we propose
approximation algorithms running in polynomial time providing web
services and community masters with applicable and near-optimal
decision making mechanisms.

The rest of paper is organized as follows. Section
\ref{s:preliminaries} describes the architecture, considered
parameters and some basic cooperative game theory concepts.
Section \ref{s:model} provides the problem statement and some numerical examples.
Section \ref{s:game_solution} presents our solution model in two
different scenarios. Section \ref{s:resutls} describes our
experiments and results. Finally, Section \ref{s:conclusion},
concludes the paper and identifies future work.

@@

\section{Preliminaries}\label{s:preliminaries}

In this section, we discuss the parameters and preliminary
concepts that we use in the rest of the paper.

\subsection{The Architecture}

Our system consists of three main types of entities working
together:

\emph{1) Web services} are rational entities\footnote{The term
rational is used here in the sense that web services are utility
maximizers} providing services to end users. They aim to maximize
their individual income by receiving enough requests from end
users. In order to increase their revenue, web services seek for
more tasks if they have the capacity and throughput to do so. Web
services can join communities to have better efficiency by
collaborating with others, to have access to higher market share,
and to have opportunity of receiving a bigger task pool from end
users. Throughout this paper, in
our equations, we refer to web services as $ws$ and to the set of
web services hosted by a given community as $C$. To simplify the
notation, sometimes we simply write $ws$ instead of $ws \in C$ to
go through the elements $ws$ of the set $C$.

\emph{2) Master Web Services} or the community coordinators, are representatives of the
communities of web services and responsible for their management.
Communities receive requests from users and aim to host a healthy
set of web services to perform the required tasks. They seek to
maximize user satisfaction by having tasks accomplished according
to the desired QoS. In fact, higher user satisfaction will bring
more user requests and increase the market share and revenue of
the community.

\emph{3) Users} generate requests and try to find the best
available services. User satisfaction is abstracted as function of
quantity and quality of tasks accomplished by a given service. 
Higher user satisfaction leads to higher trust of the community by users hence directing more requests towards that service provider.

\subsection{Web Service Parameters}\label{ws_parameters}

Web services come with different quality of service parameters.
These parameters with a short description are listed in Table
\ref{qosws}.

\begin{table}[!t]
\centering
\caption{List of web service QoS parameters.}
\begin{tabular}{|c|c||c|c|}
\hline
\textbf{Parameter} & \textbf{Definition} \\
\hline\hline
$Availability$ & Probability of being available during \\
&a time frame \\
$Reliability$ & Probability of successfully handling \\
&requests during a timeframe\\
$Successability$ & Rate of successfully handled requests \\
$Throughput$ & Average rate of handling requests \\
$Latency$ & The average latency of services\\
$Capacity$ & Amount of resources available\\
$Cost$ & Mean service fee \\
$Regulatory$ & Compliance with standards, law and rules\\
$Security$ & Quality of confidentiality \\
&and non-repudiation\\
\hline
\end{tabular}
\label{qosws}
\end{table}

We adopted a real world dataset \cite{DBLP:conf/smc/Al-MasriM09a}
which has aggregated and normalized each of these parameters to a
real value between 0 and 1. Since requests are not shared among
web services and are distributed among all of them inside a
community, each one of them comes with a given QoS denoted by
$(QoS_{ws})$. We assume that $(QoS_{ws})$ is obtained by a certain
aggregation function of the parameters considered in Table
\ref{qosws}. We use this quality output later in evaluating the
community \emph{worth} or \emph{payoff} function.

\subsection{Web Service Communities}\label{webservice-communities}

Figure \ref{fig_community} represents the architecture of web service communities. The communities are essentially an abstract model of web services. They aggregate web services and communicate with other entities such as UDDI registries and users, using identical protocols as web services. Web services join communities to increase their utility by having a larger market share and task pool. Community coordinators or master web services are responsible for community development, managing membership requests from web services and distributing user tasks among the community members. Community coordinators try to attract quality web services and keep the community as stable and productive as possible to gain better reputation and user satisfaction which results in having a higher market share for the community. The way the web services reside inside communities and how communities of web services are engineered is described comprehensively in \cite{DBLP:journals/ijebr/MaamarSTBB09}.

\begin{figure*}[!t]
\centerline{\includegraphics[width=6.25in]{community.eps}}
\caption{Architecture of Web Service communities}
\label{fig_community}
\end{figure*}

\subsection{Cooperative Game Concepts}
Cooperative game is a branch of game theory that studies
strategies of self-interested entities or agents in a setting
where those agents can increase their payoff by binding agreements
and cooperating in groups. We let $N$ be a set of players. Any
subset $S$ of $N$ can form a group called $coalition$. A
\emph{coalitional game} is a pair $G = (N, v)$, where $v$ is called
a \emph{characteristic function} $v: 2^N \to \mathbb{R}$, mapping the set of players of the
coalition to a real number $v(S)$, the worth of $S$. This number
usually represents the output or payoff or again the performance
of these players working together as coalition.  If a coalition
$S$ is formed, then it can divide its worth, $v(S)$ in any
possible way among its members. The payoff vector $x \in
\mathbb{R}^S$ is the amount of payoff being distributed among the
members of the coalition $S$. The payoff vector satisfies two
conditions:

\begin{itemize}
    \item $x_i \geq 0$ for all $i \in S$, and
    \item $\sum_{i \in S} x_i \leq v(S)$
\end{itemize}

The second criteria is called the \emph{feasibility} condition,
according to which, the payoff for each agent cannot be more than
the coalition total gain. A payoff vector is also \emph{efficient}
if the payoff obtained by a coalition is distributed amongst the
coalition members: $\sum_{i \in S} x_i = v(S)$. This definition of
the characteristic function works in \emph{transferable utility}
(TU) settings, where utility (i.e., payoff) is transferable from
one player to another, or in other words, players have common
currency and a unit of income that is worth the same for all players
\cite{myerson1991game}.

When dealing with cooperative games, two issues need to be
addressed:\\ 1. Which coalitions among all possible coalitions to form? \\
2. How to reward each member when a task is completed?\\
%
The following definitions help address these two issues.

%\subsubsection{Shapley value}

{\bf Definition 1 (Shapley value)} Given a cooperative game $(N,
v)$, the \emph{Shapley value} of player $i$ is given
by\cite{shapley_value}:
\begin{equation}\label{eq:shapley}
\phi_i(N,v) = \sum_{S \subseteq N \backslash \left\{i\right\} }
\frac{|S|! (|N|-|S|-1)!}{|N|!} (v(S \cup \left\{i\right\}) - v(S))
\end{equation}

\emph{Shapley value} is a unique and fair solution concept for
payoff distribution among the members of the coalition. It
basically rewards members with the amount of marginal contribution
they have to the coalition.

%\subsubsection{Core}

{\bf Definition 2 (Core)} A payoff vector $x$ is in the $core$ of
a coalitional game $(N, v)$ if and only if:
\begin{equation}\label{eq:core}
\forall S \subseteq N, \sum_{x_i \in S} x_i \geq v(S)
\end{equation}

The core is basically a set of payoff vectors where no subset of
players $S^\prime$ could gain more than their current payoff by
deviating and making their own coalition $\sum_{i \in S^\prime}
x_i \geq v(S^\prime)$. The sum of payoffs of the players in any
sub-coalition $S$ is at least as large as the amount that these
players could earn by forming a coalition by their own. In a
sense, it is analogue to Nash equilibrium, except that core is
about deviations from groups of entities. The core is the
strongest and most popular solution concept in cooperative game
theory. However, its computation is a combinatorial problem and
becomes intractable as the number of players increases. The core
of some real-world problem games may be empty, which means having
the characteristic function of the game $(N,v)$, there might be no
possible distribution of payoff assuring stability of subgroups.

{\bf Definition 3 (Convex cooperative games)} A game $(N,v)$ with
characteristic function $v(S)$ is convex if:
\begin{equation}\label{eq:convex}
v(S) + v(T) \leq v(S \cup T) + v (S \cap T), \forall S,T \subseteq
N.
\end{equation}

According to a classic result by Shapley \cite{S1971cores}, convex
games always have a non-empty core. We will use a variation of
convexity condition in our algorithm to check whether our
coalitions are stable.

\subsubsection*{$\epsilon$-core}\label{s:epsilon}
%\emph{$\epsilon$-Core:}
%\\
When the \emph{core} set of a game is empty, it means no coalition
of players can gain anything by deviating. An outcome would be
unstable if a coalition can benefit even by a small amount from
deviating, which is a strong requirement. In fact, in some
situations, deviations can be costly, or players may have loyalty
to their coalitions, or even it can be computationally intractable
to find those small benefits. It would only make sense for a
coalition to deviate if the gain from a deviation exceeds the cost
of performing the deviation. \emph{$\epsilon$-core} relaxes the
notion of the core, and only requires that no coalition would
benefit significantly, or within a constant amount($\epsilon$) by
deviating (see Equation \ref{eq:core}).

\begin{equation}\label{eq:core2}
\forall S \subseteq N, \sum_{x_i \in S} x_i \geq v(S) - \epsilon
\end{equation}

\subsubsection*{Coalition Structure Formation}\label{sec:coalition}

Coalition structure formation is the problem of finding the best
partition of web services into teams. In these settings, the
performance of an individual service is less important than the
\emph{social welfare} of the whole system, which is the sum of the
values of all teams. Having the game $(N,v)$, a coalition
structure $(CS)$ is \emph{socially optimal} if $CS$ belongs to set
$\operatorname*{arg\,max}_{CS} v(CS)$ where $v(CS)$ is the sum of
the values of all coalitions inside $CS$. $v(CS) = \sum_{C \in
CS}v(C)$.
%The outcome of a characteristic function game in coalition structure settings, consists of two parts; first a disjoint partition of players (agents) into coalitions, called a \emph{coalition structure} (CS) and second a \emph{payoff vector} as mentioned in cooperative game solution concepts, which distributes the value of each coalition among its members.

@@

In this section, we present  web services and community coordinator's interactions, the task distribution process and revenue models in web service communities.

\subsection{Task distribution}

As mentioned in section \ref{webservice-communities}, communities are robust service providers with well established market share and reputation. By maintaining their reputation and performance, they attract  end users which choose them as service providers to perform their tasks. The community master is characterized by a request rate $(R_C)$ from users. Each web service comes with a given QoS ($QoS_{ws}$) from which the throughput $Th_{ws}$ is excluded. Throughput is the average rate of tasks a web service can perform per time unit. Its exclusion from $QoS_{ws}$ allows us to build our analysis on the particular value of $Th_{ws}$. Thus, web services perform tasks with an average output quality of $QoS_{ws}$ and a throughput rate of $Th_{ws}$.

The community master uses a slightly modified \emph{weighted fair queuing} method to distribute tasks among its members. The goal is to allocate incoming tasks to web services with a rate matching the throughput value of $Th_{ws}$. In \emph{weighted fair queuing} method \emph{all} the input flow is multiplexed along different paths, however in our case if the input rate $(R_C)$ of the community is more than the summation of throughput values of the web services in the community, some of the input tasks will be queued and served with delay. Thus, the amount of tasks performed by community is $\sum_{ws \in C}{(Th_{ws})}$ when $\sum_{ws}{Th_{ws}} \leq R_{C}$. However, when the input rate $(R_C)$ of the community is less than the summation of throughput values of the web services in the community,
%the community has more web services having more total throughput value than community's request rate 
$(R_C)$ the \emph{weighted fair queuing} algorithm assigns a weighted task rate of $R_C \times \frac{Th_{ws}}{\sum_{ws}{Th_{ws}}}$ for each web service ($ws$) and the total rate of tasks being performed is $R_C$, the community's receiving request rate.

While distributing tasks, the community master can verify the performance, throughput and quality of service of   tasks being performed by web services. It can recognize if web services are capable of doing the amount of tasks they advertised. If for any reason there is a decline in quality metrics or throughput, the  community master will announce the new parameters and community masters and members can consider those values as benchmark for future performance calculations but also to penalize them.
In this way, players have incentive to reveal their real capabilities to profit best from the community and to avoid being penalized. In addition, the system should be dynamic enough to detect and react to web services quality metrics variation as over time web service metrics may  degrade or improve, a change that the community should adjust to. 
% Therefore its easy for the system to encourage players to be in some sense incentive compatible in the way that they would profit best by truthfully revealing their capabilities. Also it is important to be dynamic enough to consider web services which may have their quality metrics degraded or even improved over time for any reason and be able to adjust the community with new parameters.

\subsection{Community Revenue}

The communities and web services earn revenue by performing tasks. The total gain is function of quality ($QoS_{ws}$) and throughput ($Th_{ws}$) of tasks being performed. As mentioned in section \ref{ws_parameters}, $QoS_{ws}$ is obtained by a certain aggregation function of the parameters considered in Table \ref{qosws}. We have adopted a linear equal weight average over all QoS parameters listed in table \ref{qosws} excluding the $Throughput$ and $Cost$ parameters. A community has the option to weigh specific QoS parameters depending on the expectations of their clients.

The maximum potential output of a community $(PO(C))$  is an aggregation of number of tasks, times their quality, for each web service member of the community:

\begin{equation}
PO(C) = \sum_{ws \in C}{(T_{ws} \times QoS_{ws})}
\end{equation}

If the summation of throughput values ($Th_{ws}$) of community members exceeds the input task rate of the community ($R_C$) the community cannot perform at its maximum potential. It denotes the case when the community has more web services than it needs to perform the input task load. The actual output has to be normalized to the amount of tasks being performed.

\begin{equation}\label{out_c}
Out(C) = \left\{
  \begin{array}{l l}
    PO(C) & \quad \text{if $\sum_{ws}{Th_{ws}} \leq R_{C}$}\\
    PO(C) \times \frac{R_{C}}{\sum_{ws}{Th_{ws}}} & \quad \text{if $\sum_{ws}{Th_{ws}} > R_{C}$}
  \end{array} \right.
\end{equation}

The revenue function of the web service community is a linear function of $Out(C)$ with a positive constant multiplier.

\subsection{Case Study}

In this section, we analyze three numerical examples and discuss the motivation of web services and community interactions and the strategies they can adopt and the revenue they can earn adopting these different strategies.

%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 1 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
\caption{Example 1}
\label{example_1}
\centering
\begin{tabular}{c c c c}
\hline
$WS$ & $QoS_{ws}$ & $Th_{ws}$ & $Th_{ws} \times QoS_{ws}$\\
\hline
1 & 0.8 & 4 & 3.2\\
2 & 0.8 & 5 & 4.0\\
3 & 0.8 & 3 & 2.4\\
\hline
\end{tabular}
\end{table}

\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
% \caption{Three web services}
\label{example_1_2}
\centering
\begin{tabular}{c c || c c}
\hline
Community & Worth & Community & Worth\\
\hline
$\left\{1\right\}$ & 3.2 & $\left\{1,2\right\}$ & 7.2\\
$\left\{2\right\}$ & 4.0 & $\left\{1,3\right\}$ & 5.6\\
$\left\{3\right\}$ & 2.4 & $\left\{2,3\right\}$ & 6.4\\
$\left\{1,2,3\right\}$ & 8.0\\
\hline
Community $R_C$: 10\\
\hline
\end{tabular}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 1 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 2 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
\caption{Example 2}
\label{example_2}
\centering
\begin{tabular}{c c c c}
\hline
$WS$ & $QoS_{ws}$ & $Th_{ws}$ & $Th_{ws} \times QoS_{ws}$\\
\hline
1 & 0.8 & 5 & 4.0\\
2 & 0.7 & 6 & 4.2\\
3 & 0.7 & 4 & 2.8\\
\hline
\end{tabular}
\end{table}

\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
% \caption{Three web services}
\label{example_2_2}
\centering
\begin{tabular}{c c || c c}
\hline
Community & Worth & Community & Worth\\
\hline
$\left\{1\right\}$ & 4.0 & $\left\{1,2\right\}$ & 7.4\\
$\left\{2\right\}$ & 4.2 & $\left\{1,3\right\}$ & 6.8\\
$\left\{3\right\}$ & 2.8 & $\left\{2,3\right\}$ & 7.0\\
$\left\{1,2,3\right\}$ & 7.3\\
\hline
Community $R_C$: 10\\
\hline
\end{tabular}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 2 %%%%%%%%%%%%%%, %%%%%%%%%%%%%%%%%%%%%%

In the first example,  we present the case of a community with $R_C =10 $, and three web services, each having different $QoS_{ws}$ and $Th_{ws}$ values as listed in table \ref{example_1}. The worth of a community is calculated based on $Out(C)$ equation (\ref{out_c}) which is the amount of output being generated by the community. The first table  lists the web services with their aggregated $QoS_{ws}$ parameters, their task input rate while working alone, and also their  throughput value $Th_{ws}$. The second table shows all the possible communities and their respective worth. The obtained values suggest that  communities having more web services have better gain and output. However each community needs to  distribute the gain between web services. Sometimes it is impossible to share the gain between all web services in a way that no subset of them would individually gain more if they form their own group. In this example, the value community of ${ws_1}$ and ${ws_2}$ is 7.2, With ${ws_3}$ joining the community the worth increases to 8.0. However there is no way to distribute the value among web services to have  ${ws_1}$ and ${ws_2}$  earning 7.2, and ${ws_3}$ earning at least 2.4, the gain they could earn before joining the community. This fact makes the group unstable. In the second  example, shown in table \ref{example_2}, we even have situations where a web service (${ws_3}$) joining a community ($\left\{ws_1,ws_2\right\}$) decreases the value of community. The reason is, the community is already full and all tasks are almost being distributed and new community with bad quality can degrade the average quality of tasks being done by the community. In both examples, the request of joining of web service ${ws_3}$ should be rejected by the community.

%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 3 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
\caption{Example 3}
\label{example_3}
\centering
\begin{tabular}{c c c c}
\hline
$WS$ & $QoS_{ws}$ & $Th_{ws}$ & $\text{\emph{Input Task Rate}}$\\
\hline
1 & 0.8 & 10 & 5\\
2 & 0.8 & 20 & 5\\
3 & 0.8 & 30 & 5\\
\hline
\end{tabular}
\end{table}

\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
% \caption{Three web services}
\label{example_3_2}
\centering
\begin{tabular}{c c || c c}
\hline
Community & Worth & Community & Worth\\
\hline
$\left\{C_{ms_1}\right\}$ & 0 & $\left\{C_{ms_2}\right\}$ & 0\\
$\left\{C_{ms_1}, ws_1\right\}$ & 8 & $\left\{C_{ms_2}, ws_1\right\}$ & 8\\
$\left\{C_{ms_1}, ws_2\right\}$ & 16 & $\left\{C_{ms_2}, ws_2\right\}$ & 16\\
$\left\{C_{ms_1}, ws_3\right\}$ & 16 & $\left\{C_{ms_2}, ws_3\right\}$ & 24\\
$\left\{C_{ms_1}, ws_1, ws_2\right\}$ & 16 & $\left\{C_{ms_2}, ws_1, ws_2\right\}$ & 24\\
$\left\{C_{ms_1}, ws_1, ws_3\right\}$ & 16 & $\left\{C_{ms_2}, ws_1, ws_3\right\}$ & 32\\
$\left\{C_{ms_1}, ws_2, ws_3\right\}$ & 16 & $\left\{C_{ms_2}, ws_2, ws_3\right\}$ & 32\\
$\left\{C_{ms_1}, ws_1, ws_2, ws_3\right\}$ & 16 & $\left\{C_{ms_2}, ws_1, ws_2, ws_3\right\}$ & 32\\
$\left\{C_{ms_1}, C_{ms_2}, ...\right\}$ & 0 & $\left\{ws_1\right\}$ & 6.8\\
$\left\{ws_2\right\}$ & 4.2 & $\left\{ws_3\right\}$ & 6.8\\
\hline
Community $R_{C_1}$: 20 \\ Community $R_{C_2}$: 40\\
\hline
\end{tabular}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 3 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In Example 3, we consider the case of having different communities with different market share, ${R_C}$ values. Web services also have a small share of market independently, providing them with a small task pull. In these kind of scenarios, the solution considers individual maximization of payoff and also the total worth of all communities which represents the \emph{social welfare}. In this example the most efficient partition of web services is earned by having two coalitions of $\left\{C_{master_1}, ws_2\right\}$ and $\left\{C_{master_2}, ws_1, ws_3\right\}$, which yields a total value of $32 + 16 = 48$. In these types of scenarios, the goal is to reach stability, adopting a distributed approach where all players have the power of choice on the decision of whether or not they join a coalition. The communities usually start the game having some established members, encountering new web services, the communities may exchange web services and new web services would join them having at least one player gaining utility, without hurting any other participant. In this example if we initially having two coalitions of $\left\{C_{master_1}, ws_2\right\}$ and $\left\{C_{master_2}, ws_1\right\}$ and a ${ws_3}$ as new web service, ${ws_3}$ joining ${C_{master_1}}$ would hurt at least itself or $ws_2$, however ${ws_3}$ joining ${C_{master_2}}$ would not hurt any participants and ${ws_3}$ would earn more within the community and the community will have enough web services performing the incoming tasks from users.

The first two examples illustrate the fact that a community cannot simply increase its revenue by adding more web services. The web services and even community owners are autonomous agents and would deviate and be displeased about the community if new members cause a drop in their profit. The job of the community master is to attract as many quality web services it can and keep them satisfied; hence the group stability is guaranteed. 
The third example highlights another type of problem we would like to address, which is how to form best possible groups of communities, and allocate web services among communities in a way which would maximize payoff for of our agents and members already residing in the communities.
In next section, we provide collaborative game theory based algorithms for our autonomous agents, to tackle these problems and find applicable and efficient strategies for communities and web services to maximize their profit.

\section{Web Service Cooperative Games}\label{s:game_solution}

In this section, we present different web service community models
and focus on the problem of how both web services and community
masters as rational entities would adopt strategies to maximize
their payoff.

\subsection {Web Services and One Community}

In this scenario, we assume the existence of a typical community
managed by its master, and web services need to join it to be able
to get requests from the master. The community master is
characterized by a requests rate $(R_{C})$ from users. Each web
service comes with a given QoS ($QoS_{ws}$). The worth of a community
$v(C)$ is set to Out(C) based on equation \ref{out_c}.

As mentioned in previous section, the worth and output of a
community  is a function of the
throughput and provided QoS of its web service members. If the throughput rate is more than
the master's input request rate, it means the web services inside
the community are capable of serving more requests than the
demand. Considering this factor, the valuation function is
designed to balance the output performance so that it matches the
exact throughput rate and QoS the web service can provide within
the particular community.
%** In the case where the limited tasks are distributed among web services uniformly, the value of coalition would be the proportion of the average QoS times their throughput to rate of available requests. **

In this first scenario, we only consider one grand coalition and
analyze the system from the point of view of one single master web
service and a collection of web services. The master web service
decides which members can join
%or should leave%
the community and distributes the requests and income among its
community members (see Figure \ref{fig_sim1}).

\begin{figure}[!t]
\centering
\includegraphics[width=3in]{s1.eps}`
\caption{Web Services and A Grand Community}
\label{fig_sim1}
\end{figure}

>>>>

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Web Service Community \\ Learning}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%
%
%\IEEEcompsocitemizethanks is a special \thanks that produces the bulleted
% lists the Computer Society journals use for "first footnote" author
% affiliations. Use \IEEEcompsocthanksitem which works much like \item
% for each affiliation group. When not in compsoc mode,
% \IEEEcompsocitemizethanks becomes like \thanks and
% \IEEEcompsocthanksitem becomes a line break with idention. This
% facilitates dual compilation, although admittedly the differences in the
% desired content of \author between the different types of papers makes a
% one-size-fits-all approach a daunting prospect. For instance, compsoc
% journal papers have the author affiliations above the "Manuscript
% received ..."  text while in non-compsoc journals this is reversed. Sigh.

@@

% for Computer Society papers, we must declare the abstract and index terms
% PRIOR to the title within the \IEEEcompsoctitleabstractindextext IEEEtran
% command as these need to go into the title area created by \maketitle.
\IEEEcompsoctitleabstractindextext{%
\begin{abstract}
%\boldmath
Abstractttttttttttttttttt tttttttttt ttt \end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the journal you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals frown on math
% in the abstract anyway. In particular, the Computer Society does
% not want either math or citations to appear in the abstract.

@@

\section{Introduction}

\IEEEPARstart{O}{ver} Introduction

@@

\section{Preliminaries}\label{s:preliminaries}
text text

@@

text text

\section{Web Service}\label{s:web_service}

text text
